---
title: "calibration_results"
author: "Madeline Berger"
date: "5/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(paletteer)
library(here)

```

##Results from calibration
This script creates visualizations and summary statistics for the results of a calibration analysis of the BASMA burn detection algorithm (cite Gabriel?). The data were generated using ArcGis.


###Read in data
```{r}
results <- read_csv(here("raw_csv", "calibration_results.csv")) %>% 
  mutate(
    char_threshold = as.factor(char_threshold),
    cutoff = as.factor(cutoff)
  )

```


###Summary statistics
- overall mean
- average by char threshold
- average by cutoff

```{r}
#overall
average <- results %>% 
  summarize(
    avg_match = mean(match),
    sd_match = sd(match),
    min_match = min(match),
    max_match = max(match)
  )


#group by char threshold

char_stats <- results %>% 
  group_by(char_threshold) %>% 
  summarize(
    avg = mean(match),
    sd = sd(match),
    min = min(match),
    max = max(match)
  )

#group by cutoff

cutoff_stats <- results %>% 
  group_by(cutoff) %>% 
  summarize(
    avg = mean(match),
    sd = sd(match),
    min = min(match),
    max = max(match)
  )


```


###Graphs
```{r}

all_line <- results %>% 
  filter(cutoff != "3_pix") %>% 
  ggplot(aes(x = char_threshold, y = match, group = cutoff))+
  geom_line(aes(color = cutoff))+
  theme_bw()+
  labs(x = "Char Threshold", y = "Percentage of matching pixels", color = "Burn Cutoff")+
  scale_color_paletteer_d("wesanderson::GrandBudapest1")

all_line

ggsave("./figs/all_line.png", all_line, width = 8, height = 6)


bar_main <- results %>%
  filter(cutoff != "3_pix") %>% 
  filter(value == 2 | value == 3) %>% 
  mutate(
    value = as.character(value)
  ) %>% 
  ggplot(aes(x = char_threshold, y = percent, group = value))+
  geom_bar(aes(fill = value), stat = "identity")+
  facet_wrap(~cutoff)+
  theme_bw()+
  labs(x = "Char Threshold", y = "Percent match", fill = "Burn or no burn")

bar_main

ggsave("./figs/bar_main.png", bar_main, width = 8, height = 6)
```



##Repeat for any_burn 
###Read in data
```{r}
results_any <- read_csv(here("csv_data", "calibration_results_any.csv")) %>% 
  mutate(
    char_threshold = as.factor(char_threshold),
    cutoff = as.factor(cutoff)
  )

```


###Summary statistics
- overall mean
- average by char threshold
- average by cutoff

```{r}
#overall
average_any <- results_any %>% 
  summarize(
    avg_match = mean(match),
    sd_match = sd(match),
    min_match = min(match),
    max_match = max(match)
  )


#group by char threshold

char_stats_any <- results_any %>% 
  group_by(char_threshold) %>% 
  summarize(
    avg = mean(match),
    sd = sd(match),
    min = min(match),
    max = max(match)
  )

#group by cutoff

cutoff_stats_any <- results_any %>% 
  group_by(cutoff) %>% 
  summarize(
    avg = mean(match),
    sd = sd(match),
    min = min(match),
    max = max(match)
  )


```


###Graph
```{r}
#line
all_line_any <- ggplot(results_any, aes(x = char_threshold, y = match, group = cutoff))+
  geom_line(aes(color = cutoff))+
  theme_bw()+
  labs(x = "Char Threshold", y = "Percentage of matching pixels", color = "Burn Cutoff")+
  scale_color_paletteer_d("wesanderson::GrandBudapest1")

all_line_any

ggsave("./figs/all_line_any.png", all_line_any, width = 8, height = 6)


#bar
bar_any <- results_any %>%
  filter(value == 2 | value == 3) %>% 
  mutate(
    value = as.character(value)
  ) %>% 
  ggplot(aes(x = char_threshold, y = percent, group = value))+
  geom_bar(aes(fill = value), stat = "identity")+
  facet_wrap(~cutoff)+
  theme_bw()+
  labs(x = "Char Threshold", y = "Percent match", fill = "Burn or no burn")

bar_any

ggsave("./figs/bar_any.png", bar_any, width = 8, height = 6)
```
