---
title: "Adding Updated 2019 Data"
author: "Madeline Berger"
date: "5/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(sf)
library(stringr)
library(rgdal)
library(raster)
library(maptools)
library(mapview)
library(here)
```


##Part 3: Add survey data, updated

1. Read in new data
```{r}
#survey data
monitoring <- read_csv(here("survey_data","monitoring_updated.csv")) %>% 
  dplyr::select(1:5, starts_with("pv")) %>% 
  mutate(
    unique_id = paste(substr(plot_id, 2,2), resp_id, sep = "")
  )

spotcheck <- read_csv(here("survey_data","spot_check_updated.csv")) %>%
  dplyr::select(1:3, starts_with("pv")) %>% 
   mutate(
    unique_id = paste(substr(plot_id, 2,2), resp_id, sep = "")
  )

#spatial polygons
polygons <- read_sf(here(dsn = "outputs_mb"), layer = "test_all")


```

What is burned?
Monitoring data: 
- pv_burn_any == 1 means it was burned, either main or alt
- bl_error = plot is in monitoring but not baseline

Spot check
- pv_burn = if any type of burning is noticed (1 of 7)


7 types of burning measured: 
1.	 sc_burn_straw_stub "Straw or stubble looks burnt/partially burnt."
2.	sc_burn_straw_ash  "Black/grey ash on the soil surface."
3.	sc_burn_resid  "Root residues or stubble/stem residues appear burnt."
4.	sc_burn_stand_stub Standing stubble appears burnt from the top."
5.	sc_burn_grass  "Burnt grass and weeds on the plot boundaries."
6.	sc_burn_trees_burnt  "Burnt leaves/branches of the trees on the plot boundary."
7.	sc_burn_realtime "Stubble's burning in real time."

2. Create df with burn column indicating "1" if any were burned
```{r}
#join monitoring data using unique id
 #this stands for updated monitoring and spotcheck data msc

updated_2019_mon <- inner_join(polygons, monitoring, by = "unique_id") %>% 
  dplyr::select(-resp_id.x)

burn_any_only_mon <- updated_2019_mon %>% 
  dplyr::select(unique_id, resp_id.y, pv_burnt_any, geometry)

#there are 4 fewer lines - this makes sense because there were two in the `bl_error`, and since each entry had two lines for two different dates, a total of 4 should be missing. 
 
```

3. Create df with burn column indicating "1" only for main burning
```{r}
#join spot check data 
updated_2019_sc <- inner_join(polygons, spotcheck, by = "unique_id" ) %>% 
  dplyr::select(-resp_id.x)

burn_any_only_sc <- updated_2019_sc %>% 
  dplyr::select(unique_id, resp_id.y, pv_burnt_any, geometry)
#there are two less - also makes sense because there were two erros that were not in baseline and this one did not have doubles

```


4. Create df with burn column indicating "1" only for alternate burning

```{r}
#row bind both
updated_2019_mon_sc <- rbind(burn_any_only_mon, burn_any_only_sc)

#seems like there are duplicates - remove (may have lost data?)

updated_2019_mon_sc <- updated_2019_mon_sc[!duplicated(updated_2019_mon_sc$unique_id), ]

unique(updated_2019_mon_sc$pv_burnt_any)

```

5. Export new dataset
```{r}

st_write(updated_2019_mon_sc, "updated_2019_mon_sc.shp")


```

